### 2023-03-20 main.tex
i

In subsection \ref{subsection-exact}, for the case with geometry of one dimensional chain of length $L$ connected at the ends with two reservoris of parameters $(\alpha_{k})_{k=1,\ldots,N}$ and $(\beta_{k})_{k=1,\ldots,N}$, all the correlations have been written by \eqref{exactCorrelations} using integrability. When the maximal occupation of each site $\nu>1$, this nice property is lost. However, something about correlations can be said using duality. In this subsection we still consider the same geometry of \ref{subsection-exact}. As pointed out in section \ref{sectionDuality}, the dual process voids the chain. Therefore, the problem of computing the average of the duality matrix with respect to the stationary distribution is reduced to computing the absorption probabilities of dual particles, as we will clarify below.\\

>>>>

In subsection \ref{subsection-exact}, for the case with geometry of one dimensional chain of length $L$ connected at the ends with two reservoris of parameters $(\alpha_{k})_{k=1,\ldots,N}$ and $(\beta_{k})_{k=1,\ldots,N}$, all the correlations have been written by \eqref{exactCorrelations} using integrability. When the maximal occupation of each site $\nu>1$, this nice property is lost. However, something about correlations can be said using duality. In this subsection we still consider the same geometry of \ref{subsection-exact}. As pointed out in section \ref{sectionDuality}, the dual process voids the chain. Therefore, the problem of computing the average of the duality matrix with respect to the stationary distribution is reduced to computing the absorption probabilities of dual particles, as we will clarify below. In this context it is better to work agin with generators. We first write the generators for the original and the dual process and the duality matrix in the particular case of this geometry. \\
